Soss

### 2019-12-25 paper/paper.tex
abstract

\begin{abstract}
Soss is a Julia-based embedded probabilistic programming language.
\end{abstract}

@@

@@

\section{End Matter}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document. This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
This ensure that information contained therein can be more easily collected during the article metadata extraction phase, and ensures consistency in the spelling of the section heading. An example is below.

The \verb|\appendix| command is used to start the appendix sections in the document, which are indexed with letters rather than numbers. This command should be included after  the \verb|\bibliography| command, which creates the references section.

@@

\subsection{Do}

@@

\emph{Gen} \cite{Cusumano-Towner:2019} was developed independently from Soss, but takes a similar approach (and distinct from most PPLs) in its representation of a model as a function from its arguments to a "trace" (to use Gen's terminology). In both Soss and Gen's static DSL, this trace is a mapping from variable names to values. The similarity of these systems makes interoperability relatively straightforward, as demonstrated in \emph{SossGen}(\url{https://github.com/cscherrer/SossGen.jl}).

>>>>

\begin{abstract}
Soss is a probabilistic programming language embedded probabilistic programming language embedded in the Julia language. Soss represents statistical models in terms of abstract syntax trees, and uses staged compilation for on-demand generation of ``inference primitives'' (random sampling, log-density, etc) without reqquiring casual users to worry about such details.
\end{abstract}

@@

There are many approaches to building a Probabilistic Programming Language (``PPL''). Soss is distinct from most in a number of ways...

@@

@@

\subsection{Causal Interventions (``Do'' operator)}

@@

\emph{Gen} \cite{Cusumano-Towner:2019} was developed independently from Soss, but takes a similar approach (and distinct from most PPLs) in its representation of a model as a function from its arguments to a "trace" (to use Gen's terminology). In both Soss and Gen's static DSL, this trace is a mapping from variable names to values. The similarity of these systems makes interoperability relatively straightforward, as demonstrated in \emph{SossGen} (\url{https://github.com/cscherrer/SossGen.jl}).
